---
title: "index"
output: html_document
date: "2023-02-22"
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load, echo=FALSE}
library(tidyverse)
library(ds4ling)
```
## 1. Load the data set of your choice and get information about its structure (remember all code needs to be inside a knitr code chunk).

```{r, echo=FALSE}
mtcars

head(mtcars)
tail(mtcars)

#data is already tidy
```




## 3. Calculate descriptive statistics of your choice.


```{r, echo=FALSE}
summary(mtcars)

mutate(mtcars, mpg_z = (mpg - mean(mpg))/ sd(mpg))

mutate(mtcars, hp_z = (hp - mean(hp))/ sd(hp))


mtcars %>%
  select(mpg, cyl) %>%
  filter(cyl<=6 ) %>%
  t.test(mpg ~ cyl, data =.)

# I tried to analyze the mpg in vehicles that have 4 and 6 cylinders. 
#I was expecting a higher P value, as a vehicle with 6 cylinders should have a lower mpg than the one with 4, however my P value was 0.0004048

```


## 4. Select two continuous variables and fit a model to the data (bivariate regression).

```{r, echo=FALSE}

# bivariate regression model
model <- lm(mpg ~ cyl, data = mtcars)

# model 
summary(model)

```



## 5. Generate a plot that includes a regression line.

```{r}
mtcars %>% 
ggplot(aes(x = mpg, y = cyl)) + 
  geom_point(alpha = 0.05) +
  geom_smooth(method = "lm", color = "red", size = 1, se = FALSE) +
  labs(x = "Miles per galon", y = "Cylinders",
       title = "How can I save money?")
```



```{r}

mtcars %>% 
ggplot(aes(x = mpg, y = hp)) + 
  geom_point(alpha = 0.05) +
  geom_smooth(method = "lm", color = "blue", size = 1, se = FALSE) +
  labs(x = "Miles per galon", y = "Horse Power",
       title = "How can I save money 2.0")


```



## 6. Write up some general observations (1-2 paragraphs max)


I analyzed the relation between MPG, horsepower, and cylinders in the previous plots.
The plots show how the mpg increases as the cylinders and horsepower decrease.

**Conclusion to save money on gas, you must buy a car with fewer cylinders and horsepower.** 














