---
title: "index"
output: html_document
date: "2023-02-22"
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load, echo=FALSE}
library(tidyverse)
library(ds4ling)
library(languageR)
```
## 1. Load the data set of your choice and get information about its structure (remember all code needs to be inside a knitr code chunk).

```{r, echo=FALSE}
str(english)
head(english)

#data is already tidied
```




## 3. Calculate descriptive statistics of your choice.


```{r, echo=FALSE}
summary(english)


```


## 4. Select two continuous variables and fit a model to the data (bivariate regression).

```{r, echo=FALSE}

# bivariate regression model
model <- lm(RTnaming  ~ Familiarity, data = english)

# model 
summary(model)


second_model <- lm(WrittenFrequency ~ Familiarity, data = english)
summary(second_model)


```



## 5. Generate a plot that includes a regression line.

```{r}
english %>% 
ggplot(aes(x = Familiarity, y = RTnaming)) + 
  geom_point(alpha = 0.05) +
  geom_smooth(method = "lm", color = "red", size = 1, se = FALSE) +
  labs(x = "Familiarity", y = "RTnaming",
       title = "Reaction time and Familiarity")
```



```{r}

english %>% 
ggplot(aes(x = WrittenFrequency, y = RTnaming)) + 
  geom_point(alpha = 0.05) +
  geom_smooth(method = "lm", color = "blue", size = 1, se = FALSE) +
  labs(x = "WrittenFrequency", y = "RTnaming",
       title = "Reaction time and Written Frequency")


```



## 6. Write up some general observations (1-2 paragraphs max)


The scatter plots show a correlation between reaction time, familiarity and frequency.
As it can be expected, as frequency and familiarity increase, reaction time decreases.
Additionally, if we take a closer look at the p-values, between reaction time and familiarity, we obtain 1.367e-10, which is a number close to 0. 
The smaller (closer to 0) the p-value, the stronger is the evidence against the null hypothesis. 
We might still need more information to determine if this result is significant (although it looks like it), but the question is, can we reject the Null-Hupothesis?













